NumPy---Array Computation for Python

### 2019-12-21 paper.tex
Fix typo

  NumPy is the fundamental array computation library for the Python ecosystem
  \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
  It has been actively developed for over two decades and has
  more than 850 contributors, nearly 300,000 dependent repositories
  on GitHub, and millions of downloads per year.
  It is extensively used in research and teaching.
  According to a 2018 survey, NumPy is the second most commonly used machine
  learning tool among enterprises \cite{451report2018}.
  NumPy continues to evolve to meet the needs of its community, to
  remain relevant in an ever-changing computing landscape, and to be a
  fundamental pillar of support for the next decade of data science in
  Python.
  In this article, we provide an overview of the project and library
  organization,  highlight some recent technical developments, and
  outline are future plans.
\end{abstract}

>>>>

  NumPy is the fundamental array computation library for the Python ecosystem
  \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
  It has been actively developed for over two decades and has
  more than 850 contributors, nearly 300,000 dependent repositories
  on GitHub, and millions of downloads per year.
  It is extensively used in research and teaching.
  According to a 2018 survey, NumPy is the second most commonly used machine
  learning tool among enterprises \cite{451report2018}.
  NumPy continues to evolve to meet the needs of its community, to
  remain relevant in an ever-changing computing landscape, and to be a
  fundamental pillar of support for the next decade of data science in
  Python.
  In this article, we provide an overview of the project and library
  organization,  highlight some recent technical developments, and
  outline our future plans.
\end{abstract}
